Delayed effects of climate on vital rates leads to demographic divergence in Amazonian forest fragments

### 2021-05-14 doc/paper.Rmd
1st paragraph of intro

@@

Understanding how landscape structure and abiotic conditions act to influence population dynamics is central to many conceptual frameworks for studying and conserving fragmented landscapes [@didhamRethinkingConceptualFoundations2012; @driscollConceptualDomainMatrix2013].
Here we support the emerging generalization that the effects of climate drivers on demographic vital rates can be delayed [@tenhumbergTimelaggedEffectsWeather2018; @tellerLinkingDemographyDrivers2016; @eversLaggedDormantSeason2021].
We also found that the magnitude, direction, and temporal lag in demographic responses to drought differs between forest fragments and continuous forest.
Consequently, the hypothesized synergies between climate and fragmentation may be far more complex and pervasive than previously thought.

>>>>

<!--# Insert page break -->

@@

Understanding how landscape structure and abiotic conditions act to influence population dynamics is central to many conceptual frameworks for studying and conserving fragmented landscapes [@didhamRethinkingConceptualFoundations2012; @driscollConceptualDomainMatrix2013]. Our results support the emerging consensus that the effects of climatic extremes on demographic vital rates can be delayed for months or even years [@tenhumbergTimelaggedEffectsWeather2018; @tellerLinkingDemographyDrivers2016; @eversLaggedDormantSeason2021]. We also found that the delayed responses of populations in fragments can differ significantly in magnitude, direction, and lag time from those of populations in continuous forest. This suggests that the hypothesized synergies between climate and fragmentation on population dynamics [@opdam2004a; @selwood2015a; @laurance2001] are likely to be pervasive, but also far more complex than previously thought.
